---
title: "Distribute Project Notes"
author: "Lilianne Raud"
date: "March 11, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction and Data

```{r}

```

## Steps Taken

* Initially took a look at top 10,000 lines from the unzipped data (bash);

$ bzcat enwiki-20080103.main.bz2 | head -10000 > output.txt

From the output. txt file was able to determine next step:

* Get list of all articles and number of times each was revised;

run revision_count.py, from that list, compiled:

* top 1000 most revised articles;

* new mapreduce, created date, article pair with number of revisions (acbdl_redo.py), creating as complete list as the data allowed - articles_dates.csv

## * Joe explains how he created outliers.txt

* picked 67 unique articles with a specific date from outliers.txt to look at, to see if any appears to be edit-wars

* excluding the 67 unique articles from the articles_dates.csv, picked randomly another 67 articles with at least 10 edits on a single day, using mapreduce (mrjob_RandomArticle.py) and SQL 

First query created a input file for mrjob_RandomArticle.py

SELECT * FROM articles_dates
WHERE NAME NOT IN (
'Albert_Einsteir',
'Alcoholics_Anonymous',
'Anarchism',
'Anarcho-capitalism',
'Ark_of_the_Covenant',
'Arsenal_F.C.',
'Autism',
'Batman_(1989_film)',
'Bipolar_disorder',
'Black_hole',
'Black_people',
'Blaise_Pascal',
'Blitzkrieg',
'Blue_Angels',
'Blue_whale',
'Britney_Spears',
'Caffeine',
'Capitalism',
'Cat',
'Chicago_White_Sox',
'Christmas',
'Christopher_Columbus',
'Claudius',
'Color_Temperature',
'Comet_Shoemaker-Levy_9',
'Condom',
'Cyberpunk',
'Deaths_in_2003',
'Diamond',
'Dianetics',
'Doctor_Who',
'Drum_and_bass',
'Eight_queens_puzzle',
'Fermi_paradox',
'Freemasonry',
'Fundamental_Dimensions',
'Game_theory',
'Glycerine',
'Henry_Ford',
'History_of_China',
'History_of_Russia',
'Human',
'Intelligent_design',
'Jim_Morrison',
'Kilogram',
'Loch_Ness_Monster',
'March_1',
'Mathematical_economics',
'Nikola_Tesla',
'October_2003',
"People's_Republic_of_China",
'Pit_Bull',
'Scriptures',
'The_Ashes',
'The_Cure',
'Wikipedia_bugs',
'World_Trade_Center/Plane_crash',
'Down_syndrome',
'Donald_Rumsfeld',
"Barnard's_Star",
'DNA',
'Augusto_Pinochet',
'Cane_Toad',
'Astrology',
'Dinosaur',
'Abortion'
) AND COUNT >9
GROUP BY NAME;

after Mapreduce produced the random list, created a temp table:

CREATE TABLE temp_list
SELECT DATE, NAME, COUNT FROM articles_dates
WHERE NAME IN 
(
"Kangaroo","Warmia","Astronaut","Group_sex","Laura_Bush","Lagrange_equations","Astronomical_unit","Abner_Doubleday","Federal_Bureau_of_Investigation","AutoCAD","Antarctic_Treaty_System","Amoeba","Alabama","Elliptic_integral","Apollo_11","Benelux","Functional_programming","Series_(mathematics)",
"Methylenedioxymethamphetamine","Detroit_Red_Wings","Big_bang","Connective","Psychedelic","Albinism","December_10","Racism","F-117_Nighthawk","Cauchy_sequence","Aston_Martin",
"Rochester_Institute_of_Technology","Atari_2600","History_of_Germany","Cable_car_(railway)","Commodore_64","Andrew_S._Tanenbaum","Ampere","Chiba_Prefecture",
"Diocletian","London_Heathrow_Airport","AppleTalk","German_cuisine","Edgar_Rice_Burroughs","Cathode","List_of_Latin_phrases","Esperanto_grammar",
"Architectural_style","Demon","DC_Comics","December_25","Albert_Einstein","Background_radiation","Impressionism","Interlingua","Afghan","Bach_(disambiguation)","Opera_(browser)",
"Inca_Empire","Nudity","Joseph_Conrad","Berlin","Battle_of_Stalingrad","Bestiality","Eastern_Orthodox_Church","Argument_from_evolution","Diesel_engine",
"Anaximander","Brigitte_Bardot")  AND COUNT >9

and from that temp table, selected the highest count edited day for the random group:

SELECT * 
FROM (SELECT * FROM temp_list ORDER BY `Name`, COUNT DESC, DATE) X
GROUP BY `Name`;
```{r}

```


