---
title: "Article Name"
author: Lilly, Joe, Adriana, Mike, Stephanie
date: April 10, 2018
output:
  revealjs::revealjs_presentation:
    theme: night
    center: true
    transition: slide
    reveal_options:
    slideNumber: true
    previewLinks: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(revealjs)
library(tidyverse)
library(mltools)

# Pie chart 
data_pie_chart <- read.csv("intelligent_design_subjects.csv", strip.white = TRUE)
colnames(data_pie_chart) <- "subject"
data_pie_chart$count <- rep(1,nrow(data_pie_chart))
d_pie <- table(data_pie_chart)
df_pie <- data.frame(d_pie)

df_pie <- df_pie %>%
  select(subject,Freq) %>%
  filter(Freq > 1)

df_pie.percent <- df_pie %>%
  mutate(subject =subject,
         cumulatve = cumsum(Freq),
         midpoint = cumulatve - Freq /2,
         labels = paste0(round((Freq/sum(Freq))*100,1),"%"))

df_pie.percent$subject.percent <- with(df_pie.percent, paste0(subject, " ",labels))


# Visualizing time graphs
data_time <- read.csv("Intelligent_Design_articles.csv")
colnames(data_time) <- c("Design", "time", "name","ip", "comment","na")
time <- data_time$time
df_time <- data.frame(substr(time,12,16))
df_time <- df_time %>%
  mutate(id = row_number())
colnames(df_time) <- c("time","id")

df_time <- df_time %>%
  mutate(breaker = as.integer(substr(time,1,2)))


df_time$bins <- bin_data(df_time$breaker, bins=c(0, 4,9, 14, 20, 24), boundaryType = "[lorc")
```

# Data

## Superset

- Title/date pairs + fields
- 67 of them

## Outliers

- Title/date pairs + fields
- 67 of them

# Tools

## Munging

- Python's MRJob

## Visualizations

- Plotly
- RStudio
- SQL

# Statistics

## Number of comments

- Assumption
- How it was collected
- Goal

## Number of unique users

- Assumption
- How it was collected
- Goal

## Bickering Flag

- Assumption
- Result

# Visualizations

## Notable Findings

Intelligent Design Article

+ Spike in edits on December 21, 2005
+ On December 20, 2005, US court banned the teaching of Intelligent Design in public schools.
+ [Kitzmiller v. Dover Area School District]([0[[]]])
+ Most likely this spike in edits is due to this ruling the day before

## Pie Chart

```{r }
ggplot(df_pie, aes(x = "", y = Freq, fill = subject)) + geom_bar(width =1, stat ="identity")

ggplot(df_pie.percent, aes(x = "", y = Freq, fill = subject.percent)) + 
  geom_bar(width =1, stat = "identity") + 
  coord_polar(theta = "y", start =0) +
  labs(x ="", y ="", title = "Breakdown of Edits made to Different Dubjects of Intelligent Design wiki \n", fill = "Subjects")+
  ggsave("ID.subject.pie.chart.png") +
  theme(
    rect = element_rect(fill = "transparent") # all rectangles
  )


```

## Choropleth

