---
title: "<huge> Edit Wars </huge> <br> <small> When Stars and Condoms Collide </small>"
author: "<small> Lilly, Joe, Adriana, Mike, Stephanie </small>"
date: April 10, 2018
output:
  revealjs::revealjs_presentation:
    theme: night
    center: true
    transition: slide
    reveal_options:
    slideNumber: true
    previewLinks: true
---

```{r setup, include=FALSE}
#Packages
knitr::opts_chunk$set(echo = TRUE)
library(revealjs)
library(tidyverse)
library(readr)
library(pander)


#Loading data
raw.txt <- "REVISION 12 122974 Anarchism 2002-07-23T01:12:22Z Brion_VIBBER 51
CATEGORY IMAGE MAIN Syndicalism Nihilism Gustave_de_Molinari Benjamin_Tucker
Benjamin_Tucker Noam_Chomsky Peter_Kropotkin Leo_Tolstoy Leo_Tolstoy
Classical_liberalism Individualist_anarchism Individualist_anarchism
Individualist_anarchism Individualist_anarchism Libertarianism Libertarianism
Anomie Anomie Mutual_aid Mutual_aid General_strike Atheism Free_Spirit
Libertarian_socialism Libertarian_socialism Libertarian_socialism
Lysander_Spooner Capitalism Mikhail_Bakunin Self-defense Political Minarchism
Punk_rock William_McKinley Anarcho-syndicalists Karl_Marx Anarchism/Todo
Coercion John_Locke Anarcho-capitalism Anarcho-capitalism Anarcho-capitalism
Anarcho-capitalism Regicide Government Michael_Bakunin Property_damage
Max_Stirner Rudolph_Rocker Peter_Kroptkin Non-violent_resistance Proudhon
David_Friedman Voltairine_de_Cleyre TALK USER USER_TALK OTHER Pl:Anarchizm
Fr:Anarchisme Eo:Anarkismo EXTERNAL TEMPLATE COMMENT lang links: +fr, pl
MINOR 1 TEXTDATA 1169"

top1000_revisions_in_a_day <- read_csv("C:/Users/User/Google Drive/Distributed Computing/DistributedProject1.git/Outputs/top1000 revisions in a day.csv")
```

<!-- -------------------------------- -->

# Introduction

## Data

Complete edit history of all Wikipedia utill January 2008.

<ul style="list-style-type:square">
  <li> `REVISION` ***</li>
  <li> `CATEGORY` </li>
  <li> `IMAGE`</li>
  <li> `MAIN` </li>
  <li> `EXTERNAL` </li>
  <li> `TEMPLATE` </li>
  <li> `COMMENT` *** </li>
  <li> `MINOR` </li>
  <li> `TEXTDATA` </li>
</ul>

## Our project

<ol>
  <li>Edit Wars?</li>
  <li>How we found them</li>
  <li>A closer look into the articles for *Barnard's Star* and *Condoms*</li>
</ol>


# What are edit wars and how to find them?

## Munging

```{r raw data}
cat(raw.txt)
```

## Making sense of the data

```{r}
pandoc.table(head(top1000_revisions_in_a_day[,1:3], 6), justify = 'right')
```


## Datasets

- *Superset*
    * A list of every article's date and number of edits for that date.
    
    <br>
    
- *Outliers*
    * The mean number of edits per day for each article (top 5\%).
    
    <br>

- *Random*
    * Excluding the previous 67 articles, we radomly picked another 67 articles.

<!-- -------------------------------- -->

# Found something we can actually use! Now what?

## Number of comments and unique users

- Assumption
- How it was collected
- Goal

## Bickering and Vandalism 




<!-- -------------------------------- -->





